### 2016-03-13 paper/results.tex
results_section

%\hang{figure file missing}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
  \caption{}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
 \caption{}\label{fig:layered_depthmap_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_threads.png}
  \caption{}\label{fig:optical_flow_by_threads}
\end{figure}

\chen{
  There are interesting pattern in the convergence plot of optical flow estimation problem. As both FS-MF and PAE are doing binary fusion, FS-MF finds lower energy faster than PAE. The reason is as follows. Some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a much lower energy. Since there is no solution sharing in PAE model, other threads cannot share this lower energy state, and keeps working on improving its own state. On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state. To further demonstrate what is happening here, we plot the energy-time for each thread in PAE and FS-MF in figure \ref{fig:optical_flow_by_threads}. As we can see from the figure, in PAE model, one thread finds lower energy state faster than others, while other threads waste resources working at a high energy state. But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together. Same comparison holds for FS-SS and FS.
}
  \chen{
  From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state. The reason is binary fusion of solution proposals (either from others or self) is too limited to further decrease the energy due to the complexity of the problem itself. Only when multi-way fusion is used (in FS-SS and FS), it becomes possible for the energy to further decrease. This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here.
}

>>>>

%\hang{figure file missing}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
  \caption{}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
 \caption{}\label{fig:layered_depthmap_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
  \caption{}\label{fig:layered_depthmap_by_alpha}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_threads.png}
  \caption{}\label{fig:optical_flow_by_threads}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
  \caption{}\label{fig:optical_flow_by_beta}
\end{figure}

\chen{
  There are interesting pattern in the convergence plot of optical flow estimation problem. As both FS-MF and PAE are doing binary fusion, FS-MF finds lower energy faster than PAE. The reason is as follows. Some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a much lower energy. Since there is no solution sharing in PAE model, other threads cannot share this lower energy state, and keeps working on improving its own state. On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state. To further demonstrate what is happening here, we plot the energy-time for each thread in PAE and FS-MF in figure \ref{fig:optical_flow_by_threads}. As we can see from the plots, in PAE model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state. But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together. So there are more chance of finding effective proposals faster and thus the energy goes down faster. Since the solution for optical flow can be locally improved by each thread, the final merging of PAE can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model. Because FS-MF model shares information in the middle, a final merging becomes less necessary. Same comparison holds for FS-SS and FS.
}

\chen{
  To further understand the effect of solution sharing, we did two other experiments. In one experiment, we change the number of solutions each thread grabed from others from 0 to 3 (as there are 4 threads in total) while keeping others the same. The energy-time plot is shown in figure \ref{fig:optical_flow_by_beta}. In another experiment, we change the number of iterations between two consecutive solution sharing iterations as in figure \ref{fig:optical_flow_by_interval}.
}

\chen{
  From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state. The reason is binary fusion of solution proposals (either from others or self) is too limited to further decrease the energy due to the complexity of the problem itself. Only when multi-way fusion is used (in FS-SS and FS), it becomes possible for the energy to further decrease. This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here. To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy-time curve in figure \ref{fig:layered_depth_map_by_alpha}.
}
